Holomorphic field theories and higher algebra

### 2024-09-10 draft.tex
added reminders on what to include in completing the paper

\subsubsection{Holomorphic $\sigma$-models}

If $X,Y$ are any two complex manifolds there is a theory whose fields consist, in part, of the derived moduli space of smooth maps $\RR {\rm Map}(X,Y)$ and whose equations of motion dictate that such maps be holomorphic.
This is a nonlinear generalization of the $\beta\gamma$ system we just introduced.

The precise space of fields, in cohomological degree zero, consist of pairs $(\gamma, \beta)$ where $\gamma \colon X \to Y$ is a smooth map and 
\[
\beta \in \Omega^{n,n-1}(X, f^* \T^*_Y) 
\]
where $\T^*_Y$ is the holomorphic cotangent bundle of $Y$. 
The action functional is the familiar one
\beqn
\int_X \beta \dbar \gamma .
\eeqn 
Solutions to the equations of motion describe, in part, holomorphic maps $X \to Y$, but there is also derived information contained in this model.

@@

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
\beqn
\mu \in \Omega^{0,1}(X,\T_X) .
\eeqn 
A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
The action functional is very similar to the Chern--Simons action
\beqn
S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
\eeqn
In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
\beqn
\dbar \mu + \frac12 [\mu,\mu] = 0 ,
\eeqn
where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.

@@

\owen{discuss OPE and explain the shifted Poisson structure}

@@

\owen{We should review BW results and subsequent improvements by Gaiotto et al and Wang}

>>>>

Holomorphic BF theory is easy to formulate classically, but it can admit peculiar properties at the quantum level.
For example, in \cite{semichiral} it is shown that on $X = \C^2$ the quantization of holomorphic BF theory is almost topological.\footnote{More precisely, the divergence-free part of the stress tensor is rendered cohomologically trivial to first-order in perturbation theory.}

@@

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira spencer theory is a $(0,1)$ form on $X$ with values in the holomorphic tangent bundle $\T_X$
\beqn
\mu \in \Omega^{0,1}(X,\T_X) .
\eeqn 
A crucial assumption of this model is that we must assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning its divergence vanishes ${\rm div}_\Omega \mu = 0$.
The action functional is very similar to the Chern--Simons action
\beqn\label{eqn:KS1}
S(\mu) = \int_X \left(\frac12 \mu \dbar \del^{-1} \mu + \frac13 \mu^3\right) .
\eeqn
In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
Forgoing the apparent global issues, we can still apply formal variational calculus to the action to obtain the equation of motion
\beqn
\dbar \mu + \frac12 [\mu,\mu] = 0 ,
\eeqn
where $[-,-]$ is the Schouten--Nijenhuis bracket (which reduces to just the natural bracket when restricted to vector fields).
The reader can recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.

A typical scalar field theory is the free boson which exists on any Riemannian manifold $\Sigma$.
Its action functional is simply $\int_\Sigma \phi \triangle \phi$ where $\phi$ is a smooth function on $\Sigma$.
We saved this example for last since its holomorphic analog is a bit more elusive than the previous examples.

We start with complex dimension $1$.
The usual scalar field theory can be written as $\int_{\Sigma} \phi \del \dbar \phi$, where $\Sigma$ is a Riemann surface.
This theory is not holomorphic, but we can force it to be by demanding the constraint $\dbar \phi = 0$.
Importantly, this constraint is \textit{not} imposed by an equation of motion.
When we do this, we can express the action functional in terms of the $(1,0)$-form $\alpha \in \Omega^{1,0}(\Sigma)$ as
\beqn\label{eqn:scalar1}
\int \alpha \dbar \del^{-1} \alpha .
\eeqn
This is formally similar to the kinetic term in the action functional of Kodaira--Spencer theory \eqref{eqn:KS1}.

There is a higher-dimensional analog of the chiral sector of the scalar field.
Suppose that $X$ is a complex manifold of \textit{odd} dimension $2n+1$.
The fields are certain $(n+1,n)$-forms $\alpha \in \Omega^{n+1,n}(X)$ which satisfy the constraint
\beqn
\del \alpha = 0.
\eeqn
Note that when $n=0$, so $X = \Sigma$ is simply a Riemann surface, this constraint is automatic.
The action functional is the same \eqref{eqn:scalar1}.
When $n=1$ this is identical to the kinetic part of the Kodaira--Spencer action.\footnote{Indeed, when $X$ is a Calabi--Yau three-fold there is an isomorphism $\Omega^{2,1}(X) \simeq \Omega^{0,1}(X, \T_X)$.}
Generally, this theory is the holomorphic part of a higher-form scalar theory, with action
\beqn
\int_X \|C\|^2 \op{dvol} = \int_X C \d \star \d C , \quad C \in \Omega^{2n+1}(X) .
\eeqn
For more details we refer to \cite{GRWwzw}.

@@

\owen{discuss OPE, explain the shifted Poisson structure, and mention $\lambda$-brackets}

@@

\owen{We discussed having the following:
\begin{itemize}
\item Quick overview for topological field theories (=analytic content is de Rham complex): 
\begin{itemize}
\item Axelrod-Singer-Kontsevich method via compactified configuration spaces (Fulton-MacPherson) guarantees no divergences for individual graphs and organizes/clarifies analysis of anomalies
\item Explain what this means in terms of Theorem 3.6 (Elliott-Safronov) and Corollary 4.6 (about existence of functorial field theories)
\item Mention the connection with formality of the $E_d$ operads and related outgrowths in topology 
\end{itemize} 
\item Overview the history of the holomorphic case, with citations
\item Describe a version of Minghao's results (and those of Gaiotto {\it et al}) that emphasizes no divergences for individual graphs and the consequences for anomalies (e.g., relevant wheels for 1-loop and higher loop generalization via Laman graphs)
\item Explain what this means in terms of Theorem 3.9 (existence of polydiscs algebras)
\end{itemize}}
